The promise of community-driven preprints in ecology and evolution

### 2024-05-02 ms/ms.qmd
Added some numbers and details to legend fig 1

```{r, fig-summary}
#| label: fig-summary
#| fig-cap: Summary of articles posted to *EcoEvoRxiv*. A) Number of articles (preprints and postprints) published monthly to *EcoEvoRxiv* between 2018 and 2023. *EcoEvoRxiv* was established in June 2018 before the soft launch in November 2018; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv*; D) Types of articles accepted on *EcoEvoRxiv*. E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
#| echo: false
#| warning: false
#| message: false

@@

  # Summary of the data
  sum_taxa <- data2  %>% dplyr::select(all_of(cols))  %>% apply(., 2, sum, na.rm = TRUE)  %>% data.frame()   %>% rownames_to_column(var = "taxa")  %>% rename("n" = ".")  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))

  # Use data to create a pir chart and clean up colour palette

@@

##---------------------##
# Types pf preprints
##---------------------##
# Summary of the data
  sum_types <- preprints  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))

  p4 <- ggplot(sum_types, aes(x = "", y = perc, fill = type)) +
    geom_col(color = "black") +
    geom_label_repel(aes(label = labels),
              position = position_stack(vjust = 0.6),
            show.legend = FALSE) +
    scale_fill_viridis_d() +
    coord_polar(theta = "y") + 
    theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")

>>>>

```{r, fig-summary}
#| label: fig-summary
#| fig-cap: Summary of articles posted to *EcoEvoRxiv*. A) Number of articles (preprints and postprints) published monthly to *EcoEvoRxiv* between 2018 and 2023. *EcoEvoRxiv* was established in June 2018 before the soft launch in November 2018. Notable milestones include when *EcoEvoRxiv* transitioned to the California Digitial Library (CDL), the acceptance of Spanish and Portuguese preprints and postprints and when the first IUCN Redlist Ecosystem report was accepted; B) Countries that are posting articles (preprints and postprints) to *EcoEvoRxiv* as inferred from the country of affiliation of the submitting author; C) Taxa used / covered in the articles posted to *EcoEvoRxiv* (*n* = 1080); D) Types of preprints accepted on *EcoEvoRxiv* (*n* = 620). E) Career stage of authors posting to *EcoEvoRxiv* along with the gender of the submitting author.
#| echo: false
#| warning: false
#| message: false

@@

  # Summary of the data
  sum_taxa <- data2  %>% dplyr::select(all_of(cols))  %>% apply(., 2, sum, na.rm = TRUE)  %>% data.frame()   %>% rownames_to_column(var = "taxa")  %>% rename("n" = ".")  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
  #sum(sum_taxa$n) #1080
  # Use data to create a pir chart and clean up colour palette

@@

##---------------------##
# Types pf preprints
##---------------------##
# Summary of the data
  sum_types <- preprints  %>% tabyl(type_of_preprint)  %>% rename("type" = type_of_preprint, "n" = n)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))
  sum(sum_types$n) #620
  p4 <- ggplot(sum_types, aes(x = "", y = perc, fill = type)) +
    geom_col(color = "black") +
    geom_label_repel(aes(label = labels),
              position = position_stack(vjust = 0.6),
            show.legend = FALSE) +
    scale_fill_viridis_d() +
    coord_polar(theta = "y") + 
    theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")
